\section{Fools Garden - Lemon Tree}
Capo on 4th fret\\
\\
Intro\\
\textbf{Am Em Am Em Dm Em Am  [ Em Am ]}\\
\\
Verse\\
I'm sitting here in a boring room, \textbf{Am Em}\\
It's just another rainy sunday afternoon.\\
I'm wasting my time, I got nothing to do.\\
I'm hanging around, I'm waiting for you,\\
But nothing ever happens - and I wonder. \textbf{Dm Em Am [Em Am]}\\
\\
\\
I'm driving around in my car, \textbf{Am Em}\\
I'm driving too fast, I'm driving too far.\\
I'd like to change my point of view\\
I feel so lonely, I'm waiting for you\\
But nothing ever happens - and I wonder. \textbf{Dm Em Am [Em Am]}\\
\\
Chorus\\
I wonder how, I wonder why \textbf{C G}\\
Yesterday you told me 'bout the blue blue sky \textbf{Am Em}\\
And all that I can see is just a yellow lemon tree. \textbf{F G C G7}\\
I'm turning my head up and down, \textbf{C G}\\
I'm turning turning turning turning turning around \textbf{Am Em}\\
And all that I can see is just a yellow lemon tree. \textbf{F F\texttt{\#}dim G G7}\\
\\
Interlude \\
\textbf{Am  Am  Em  Em  Am  Am  Em  Em  Dm  Dm  Em  Em  Am [Em Am]}\\
Dam     dadoudi....\\
\\
Verse\\
I'm sitting here, I miss the power. \textbf{Am Em}\\
I'd like to go out, taking a shower,\\
But there's a heavy cloud inside my head.\\
I feel so tired, put myself to bed,\\
Where nothing ever happens - and I wonder. \textbf{Dm Em Am Em Am}\\
\\
Bridge\\
Isolation - Is not good for me, \textbf{E Am}\\
Isolation - I don't want to sit on a lemon tree. \textbf{G C E}\\
\\
Verse\\
I'm stepping around in a desert of joy \textbf{Am Em}\\
Baby anyhow I'll get another toy\\
And everything will happen - and I will wonder. \textbf{Dm Em Am Em Am}\\
 \\
Chorus\\
I wonder how, I wonder why \textbf{C G}\\
...\\
 \\
I wonder how, I wonder why \textbf{C G}\\
Yesterday you told me 'bout the blue blue sky \textbf{Am Em}\\
And all that I can see, And all that I can see, \textbf{F G C G7}\\
And all that I can see is just a yellow lemon tree. \textbf{F G G7 C}\\
\begin{verbatim}
Am    x02210
C     x32010
Dm    xx0231
E     022100
Em    022000
F     133211
F#dim xx1212
G     320033
G7    320001
\end{verbatim}
\newpage


